High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-12 paper/main.tex
made requested edits to fig 9 reference

Having established that patterns of high-order correlations are
informative to decoders, we next wondered which specific networks of
brain regions contributed most to these patterns.  As a representative
example, we selected the kernel parameters that yielded decoding
accuracies that were the most strongly correlated (across conditions
and orders) with the average accuracies across all of the
kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
template, the best-matching kernel was a Laplace kernel with a width
of 50 (Fig.~\ref{fig:kernels}d; also see Fig.~\pca).  We used this kernel to compute a
single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
experimental condition.  We then used Neurosynth~\cite{RubiEtal17} to
compute the terms most highly associated with the most strongly
correlated pairs of regions in each of these matrices
(Fig.~\ref{fig:neurosynth}; see Reverse inference).

@@

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
and has been deposited in the Zenodo database under accession code
\href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
The source data underlying Figs. 2-6 and Supplementary Figs. S1-S9 are
provided as a Source Data file. Source Data are provided with the
manuscript. The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.

>>>>

Having established that patterns of high-order correlations are
informative to decoders, we next wondered which specific networks of
brain regions contributed most to these patterns.  As a representative
example, we selected the kernel parameters that yielded decoding
accuracies that were the most strongly correlated (across conditions
and orders) with the average accuracies across all of the
kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
template, the best-matching kernel was a Laplace kernel with a width
of 50 (see Kernel-based approach for computing dynamic correlations and Fig.~\pca).  We used this kernel to compute a
single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
experimental condition.  We then used Neurosynth~\cite{RubiEtal17} to
compute the terms most highly associated with the most strongly
correlated pairs of regions in each of these matrices
(Fig.~\ref{fig:neurosynth}; see Reverse inference).

@@

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
and has been deposited in the Zenodo database under accession code
\href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
The source data underlying Figures~2--6 and Supplementary Figures~S1--S9 are
provided as Source Data files. Source Data are provided with the
manuscript. The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.
